---
title: "Prelim-analysis"
format: html
editor: visual
---

## Overview
We put out 20 AudioMoth recorders around the north country to see how the animal 
soundscape changes during a total solar eclipse.

For a first pass at data analysis for the 2024 Northeast Natural History Conference,
we used the [BirdNET-Analyzer](https://github.com/kahst/BirdNET-Analyzer) to attempt to identify the species present in the audio files.

Output from BirdNET is a bunch of .csv files. I'd like to be able to pull them all into one big data frame.

Let's set things up

```{r}
rm(list = ls())
library(tidyverse)
library(lubridate)
library(here)
```

Let's see if we can create a loop that will do it.

First, create a path to the folder with the data in it. [Here's a good link](http://jenrichmond.rbind.io/post/where-is-here/) that shows basically what I want to do, no loop required.

```{r}
filefolder <- normalizePath("/Volumes/NoCo Audio/Eclipse 2024/A002_SD013/NENHC output") #file path to folder with BirdNET output

files <- dir(filefolder, pattern = "*.csv")

```

Now use map() to take the list run read_csv on all of them and bind them together

```{r, results='hide'}
#temporarily set working directory to path where files are located
setwd(filefolder)
A002_SD013 <- files %>%  
  map(read_csv) %>% 
  reduce(rbind)

#return to home directory
setwd("/Users/barthelmess/Library/CloudStorage/Dropbox/R/Eclipse-Listening-Project")
```
Next see if we can strip the date time from the filename

```{r}
A002_SD013 <- A002_SD013 %>% mutate(
  Date_time = substring(filepath, 45, 59)
)
```
Now make into a date
```{r}
A002_SD013$Date_time<-ymd_hms(A002_SD013$Date_time)
```

And write the file so that we don't have to go through all of this again!

```{r}
write.csv(A002_SD013, here("Data", "A002_SD013.csv"), row.names = FALSE)
```



